Life stresses mediate an association between negative perception of activism and a decision never to participate
======

## Variables
![Take a picture of the page from my notebook, and put it here.]()

questions 4c, 7c and 8

The questionnaire requested that question 4c only be answered by people who had
answered with one of the two "No" responses to question 8, so we used only the
subset of the data for which question 8 was one of these no responses. We thus
had a binary participation variable, `no.never`, which was true if the
participant said she would never participate and false if she said that she
had not participated but (would like to ?).

For both questions 4c and 7c, almost people checked either zero or one box.
For simplicity, we simply checked whether at least one of the respective
groups of check marks was checked. Thus, our life stress variable,
`has.life.stress`, was true if at least one of question 4c's boxes was checked
and false if none was checked. Similarly, our variable for negative perception
of activism, `has.negative.perception`, was true if at least one of 7c's
boxes was checked and false if none were.

We chose variable names that start with the word "has" so that it would be less
confusing to talk about, but both groups obviously have both life stresses
and some negative perception of activism; if these names bother you, mentally
switch the "has" to "has more".

## Results
```{r summary, echo = F}
sample.probabilities
```

```{r blah}
print(sample.probabilities)
#print(summary(logit.alternative))
#print(anova(logit.alternative, logit.null))
print(summary(ols.alternative))

```

## Not experimental
We intuitively suspect a particular direction of causality and have fit models
that suggest that direction, but the questionnaire gives us no formal idea
about the direction of causality; for example, it could be that the choice never
to participate leads to overstatement of reasons against participation and
of life stresses.

## Ideas for future study
We ignored which boxes people checked for questions 4c and 7c. It may be
informative to see how the particular box that was checked relates to
the question 8 result or other results.
